taxize - taxonomic search and retrieval in R

### 2013-05-29 inst/doc/taxize_withcode.Rnw
Added a new appendic. Also create a .Rnw file for both appendices.

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhabs data must be aggregated to a joint taxomic level.

taxize can help in this data-cleaning step, providing a reproducible workflow. Here we illustrate this on a small fictitious example.

@@

\begin{itemize}
    \item{Appendix A.} A complete reproducible workflow, from a species list to a phylogeny, and a species distribution map. 
\end{itemize}

>>>>

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two data tables may contain species information on different taxonomic levels and perhabs data must be aggregated to a joint taxomic level.

taxize can help in this data-cleaning step, providing a reproducible workflow. This is illustrated on a small fictitious example in appendix B.

@@

\begin{itemize}
    \item{Appendix A.} A complete reproducible workflow, from a species list to a phylogeny, and a species distribution map. 
    \item{Appendix B.} Matching species tables with different taxonomic resolution.
\end{itemize}
